Quantifying the Impact \\ of Performance Improvements and Cost Reductions \\ from 20 years of Light-Emitting Diode Manufacturing

### 2021-02-11 SPIE/article/main.tex
further edits

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\setlength{\extrarowheight}{2pt}
\usepackage{chemformula}

@@

    Within just 25 years of the introduction of first commercial white light-emitting diodes (LED), the solid state lighting industry has become a rare success story in the global drive for the transformation of energy systems. Today, the solid-state lighting markets in the US and the EU together are valued at 58.7 Bn.\$(2020) \cite{gvr2020market_us,gvr2020market_eu} with general illumination market penetration exceeding 50\% \cite{eu2019impactass,stratunl2018}. Estimates for the electrical energy saved annually from SSL adoption ranges from 131 TWh/year in 2020 for the EU \cite{eu2019impactass} to 442 TWh/year in 2020 for the US \cite{yamada2015adoption,guidehouse2020adoption}, which is on par with the amount of energy produced by all deployed solar photovoltaic installations in these regions. Legislation aimed at increasing the adoption of solid-state light sources that has been implemented around the world creates favorable conditions for further expansion of the industry. However, this revolution in lighting would not have been possible without dramatic improvements in the overall LED device efficiency and reductions in LED manufacturing costs. In last twenty years, efficiency has increased by three orders of magnitude [CHECK IF THAT IS APPROPRIATE, AS "ORDERS OF MAGNITUDE" FOR VARIABLES MEASURED IN PERCENTAGES ARE NOT VERY MEANINGFUL], while manufacturing costs have fallen by two orders of magnitude.

@@

    \begin{figure} [ht]
        \begin{center}
            \includegraphics[width=0.85\textwidth]{SPIE/article/breakthroughs_efficiency.pdf}
        \end{center}
        \caption{Impact of technology breakthroughs and manufacturing process improvements on historical developments in sub-efficiencies of phosphor-converted warm white light-emitting diodes with test currents of at least $I_\text{test}=350$mA. The overall lamp efficiency $\eta_L$ is displayed as the rightmost column. This figure takes as inputs the state-of-the-art sub-efficiencies discussed in section \ref{sec:methods}. Horizontal colored bars give state-of-the-art sub-efficiencies for five years: \textcolor{blue}{1997}, \textcolor{teal}{2002}, \textcolor{orange}{2010}, \textcolor{magenta}{2016} and \textcolor{red}{2020}. Colored annotation "N/A" indicates that the sub-efficiency of the corresponding year cannot be computed for the following reasons: V$_\text{f}$E, Droop: depend on current, which was below 350mA at the time; CE, SE: warm white spectrum LEDs not available at the time. Physical limits are indicated by black horizontal bars. The possible range for the physical limit of V$_\text{f}$E exceeds 100\% and depends on electrical device parameters, which are discussed in \cite{david2016electrical}. The range of this limit is indicated by an upward pointing black arrow. Efficiency acronyms are listed in table \ref{tab:eff}. Data for historical improvements of sub efficiencies from Weinold et al. \cite{weinold2020technology}}
        \label{fig:efficiency}
    \end{figure}

@@

    A preliminary analysis of components of the cost model suggests that an increase in wafer size in the manufacturing process is responsible for the largest part of the cost reduction. The number of die per wafer associated with this is displayed in the inset plot of figure \ref{fig:cost}. The wafer diameter used in production has been steadily increasing since 2002. The model assumes diameters and associated number of die per wafer  $d(2002)=50$mm$\rightarrow851$ to $d(2020)=200$mm$\rightarrow26,838$. Note that the decrease in exclusion zone and cutting width also contribute to the increase in die per wafer.

    As the number of die per wafer increases, the packaging steps carry a larger share of the total cost. This is because these steps are limited by the throughput of the associated equipment. The wafer processing steps are limited by the number of die per wafer and only to a lesser extend the throughput of equipment.

    XXX some numbers from the figure

\begin{figure} [ht]
    \begin{center}
        \includegraphics[width=0.85\textwidth]{SPIE/article/costmodel_calibration.pdf}
    \end{center}
    \caption{Left panel: Modeled manufacturing cost for low power classical chip architecture (lateral current spreading) the specified architecture of light-emitting diode packages split by manufacturing step category. Right panel: The number of die per wafer corresponding to wafers of different sizes, associated street width and exclusion zone. Calculated using approximations introduced by de Vries \cite{deVries2005}.}
    \label{fig:cost}
\end{figure}

@@

    We also construct the manufacturing cost model for low-power and mid-power LED packages produced at a virtual US location using state-of-the-art equipment. We estimate that the cost of LED manufacturing in these conditions has dropped from 1.11$(2020) in 2002 to 0.05$(2020) in 2020, a 95.5\% decrease. The largest contribution to overall historical cost reductions came from increase in wafer size. The largest remaining contributor to the manufacturing cost is the LED packaging, contributing 60\% to the cost structure in 2020.

>>>>

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{tabularx}
\usepackage{wrapfig}
\setlength{\extrarowheight}{2pt}
\usepackage{chemformula}

@@

    Within just 25 years of the introduction of first commercial white light-emitting diodes (LED), the solid state lighting industry has become a rare success story in the global drive for the transformation of energy systems. Today, the solid-state lighting markets in the US and the EU together are valued at 58.7 Bn.\$(2020) \cite{gvr2020market_us,gvr2020market_eu} with general illumination market penetration exceeding 50\% \cite{eu2019impactass,stratunl2018}. Estimates for the electrical energy saved annually from SSL adoption ranges from 131 TWh/year in 2020 for the EU \cite{eu2019impactass} to 442 TWh/year in 2020 for the US \cite{yamada2015adoption,guidehouse2020adoption}, which is on par with the amount of energy produced by all deployed solar photovoltaic installations in these regions. This revolution in lighting would not have been possible without dramatic improvements in the overall device efficiency and reductions in manufacturing costs.

@@

    \begin{figure} [ht]
        \begin{center}
            \includegraphics[width=0.85\textwidth]{SPIE/article/breakthroughs_efficiency.pdf}
        \end{center}
        \caption{Impact of technology breakthroughs and manufacturing process improvements on historical developments in sub-efficiencies of phosphor-converted warm white light-emitting diodes with test currents of at least $I_\text{test}=350$mA. The overall lamp efficiency $\eta_L$ is displayed as the rightmost column. This figure takes as inputs the state-of-the-art sub-efficiencies discussed in section \ref{sec:methods}. Horizontal colored bars give state-of-the-art sub-efficiencies for five years: \textcolor{blue}{1997}, \textcolor{teal}{2002}, \textcolor{orange}{2010}, \textcolor{magenta}{2016} and \textcolor{red}{2020}. Colored annotation "N/A" indicates that the sub-efficiency of the corresponding year cannot be computed for the following reasons: V$_\text{f}$E, Droop: depend on current, which was below 350mA at the time; CE, SE: warm white spectrum LEDs not available at the time. Physical limits are indicated by black horizontal bars. The possible range for the physical limit of V$_\text{f}$E exceeds 100\% and depends on electrical device parameters, which are discussed in \cite{david2016electrical}. The range of this limit is indicated by an upward pointing black arrow. Efficiency acronyms are listed in table \ref{tab:eff}.}
        \label{fig:efficiency}
    \end{figure}

@@

    A preliminary analysis of components of the cost model suggests that an increase in wafer size in the manufacturing process is responsible for the largest part of the cost reduction. The number of die per wafer associated with this is displayed in the inset plot of figure \ref{fig:cost}. The wafer diameter used in production has been steadily increasing since 2002. The model assumes diameters and associated number of die per wafer  $d(2002)=50$mm$\rightarrow851$ to $d(2020)=200$mm$\rightarrow26,838$. Note that the decrease in exclusion zone and cutting width also contribute to the increase in die per wafer. As the number of die per wafer increases, the packaging steps carry a larger share of the total cost. This is because these steps are limited by the throughput of the associated equipment. The wafer processing steps are limited by the number of die per wafer and only to a lesser extend the throughput of equipment.

    \begin{table}[h!]
        \caption{Manufacturing cost of low-power classical chips (lateral current spreading) estimated with the cost model introduced in section \ref{sec:methods}. Relative contributions of different manufacturing process steps are shown in figure \ref{fig:cost}.}
        \bigskip
            \centering
            \begin{tabularx}{\textwidth}{|l|l|X|X|X|}
            	\hline
            		\textit{Year} & \textit{Unit} & \textit{Cost (Wafer Proc.)} & \textit{Cost (Packaging)} & \textit{Total Cost} \\
                \hline
                    2002 & \$(2020) & 0.975 & 0.138 & 1.113 \\
                \hline
                    2002-2012 & \% & -62.05 & -47.10 & -90.12 \\
                \hline
                    2012 & \$(2020) & 0.037 & 0.073 & 0.110 \\
                \hline
                    2012-2020 & \% & -67.56 & -36.98 & -47.27 \\
                \hline
                    2020 & \$(2020) & 0.012 & 0.046 & 0.058 \\
                \hline
            \end{tabularx}
            \label{tab:cost}
        \end{table}

@@

    We also construct the manufacturing cost model for low-power and mid-power LED packages produced at a virtual US location using state-of-the-art equipment. We estimate that the cost of LED manufacturing in these conditions has dropped from 1.11\$(2020) in 2002 to 0.05\$(2020) in 2020, a 95.5\% decrease. The largest contribution to overall historical cost reductions came from increase in wafer size. The largest remaining contributor to the manufacturing cost is the LED packaging, contributing 60\% to the cost structure in 2020.
